Stack Safety is a Security Property

### 2021-04-13 tex/main.tex
Comments and polishing on abstract / intro

We propose formal criteria for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state'').
% These properties are sensible even in the presence of
% abnormal control flow.\apt{Is this important enough to mention here?}
% BCP: I think not in the abstract, but maybe in the intro.
% We further apply\apt{what does this mean? we didn't
%  invent it} a straightforward notion of
% ``well-bracketed control flow'' that restricts control flow to the
% typical pattern of matched calls and returns.
%
We argue that these criteria match common intuitions (1) by showing that
they are violated by a variety of intuitively unsafe examples and (2) by
using property-based random testing to check that appropriate variants of
the criteria are actually enforced by the stack-safety ``micro-policies''
proposed by~\citet{DBLP:conf/sp/RoesslerD18} (and {\em not} enforced by
broken versions of these enforcement mechanisms).  Specifically, Roessler
and Dehon's ``eager'' micro-policy, which catches violations as early as
possible, enforces the basic ``stepwise'' versions of our confidentiality
and integrity properties. Their more performant ``lazy'' micro-policy
does not, but inspires weaker, more extensional ``observational'' variants of the
properties. While we do not rule out other enforcement mechanisms, our
definitions are strongly informed by micropolicy systems, especially
our attacker model.
\sna{Seems like the best place to admit we're tied to micropolicies is
  while discussing micropolicies.}

\bcp{We should mention stack data and coroutines, I think?  Maybe in the
  context of an expectation-lowering hedge, like:}%
For the sake of concreteness, most of our presentation assumes a RISC-V
machine architecture with a basic subroutine calling convention, where
parameters are passed in registers. We also show how to accomodate
stack-allocated parameter passing and coroutines.

\bcp{this is also a
  good place to admit that our definitions are tuned for micropolicies, if
  we can find a succinct way to say it.}
\sna{See above.}

@@

>>>>

We propose formal criteria for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state'').
% These properties are sensible even in the presence of
% abnormal control flow.\apt{Is this important enough to mention here?}
% BCP: I think not in the abstract, but maybe in the intro.
% We further apply\apt{what does this mean? we didn't
%  invent it} a straightforward notion of
% ``well-bracketed control flow'' that restricts control flow to the
% typical pattern of matched calls and returns.
%
We argue that these criteria match common intuitions (1) by showing that
they are violated by a variety of intuitively unsafe examples and (2) by
using property-based random testing to check that appropriate variants of
the criteria are actually enforced by the stack-safety ``micro-policies''
proposed by~\citet{DBLP:conf/sp/RoesslerD18} (and {\em not} enforced by
broken versions of these enforcement mechanisms).  Specifically, Roessler
and Dehon's ``eager'' micro-policy, which catches violations as early as
possible, enforces the basic ``stepwise'' versions of our confidentiality
and integrity properties. Their more performant ``lazy'' micro-policy
does not, but inspires weaker, more extensional ``observational'' variants of the
properties. While we do not rule out other enforcement mechanisms, our
definitions are strongly informed by micropolicy systems, especially
our attacker model.

For the sake of concreteness, most of our presentation assumes a RISC-V
machine architecture with a basic subroutine calling convention (passing
parameters in registers) and a micropolicy-like enforcement mechanism. We
also show how to accomodate stack-allocated parameter passing and
coroutines.

\bcp{this is also a
  good place to admit that our definitions are tuned for micropolicies, if
  we can find a succinct way to say it.}
\sna{See above.}
\bcp{I added it to the last paragraph (which is pretty close to the preceding
  paragraph :-)  We should follow this up with some discussion in the (new)
  Assumptions section about how different enforcement mechanisms (us,
  StkTokens, maybe others) adopt different perspectives on what the stack is
for and how it is organized and so lead to somewhat different notions of
low-level safety.}

@@

\bcp{I would still advocate splitting this into two sections, just so the
  transition from one to the other and the division of responsibility are
  clear.  The first section could be called ``What is 'the Stack'?'' instead
of ``Assumptions'' if we want.}
